Congestion Control Aware Queuing

### 2019-10-22 tex/paper.tex
Remove private script

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/cocoa_illustration_too_much.pdf}
\caption{If the buffer is too large, loss-based \glspl{cca} will keep a unnecessary standing queue. This queue is unnecessary since it is not generally required to achieve full link utilization.}
\label{fig:tooMuch}
\end{figure}

@@

We evaluate \gls{cocoa} using the \texttt{py-virtnet} (\url{https://github.com/CN-TU/py-virtnet}) toolkit to build a virtual network using Linux's network namespaces. We initialize the buffer size for \gls{cocoa} to 100 packets per flow like in fq.

\begin{figure}[h]
%\subfloat[Throughput of the fq \gls{qdisc}\label{fig:fqThroughput}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
%\subfloat[Delay of the fq \gls{qdisc}.\label{fig:fqDelay}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow that is managed by fq at the bottleneck. The initial bandwidth is 20\,Mbit/s but it is halved after 30\,s. The delay is 10\,ms. It is clear that there is a standing queue and after the bandwidth halves, the minimum delay is 100\,ms even though 10\,ms would be possible.}
\label{fig:fq}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughput}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_10_20_60_0.5_bw_1571241047054.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelay}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_10_20_60_0.5_bw_1571241047054.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow that is managed by \gls{cocoa} at the bottleneck. The initial bandwidth is 20\,Mbit/s but we halve it after 30\,s. The delay is 10\,ms. \gls{cocoa} manages to keep the queuing delay minimal while achieving the same throughput as with an oversized buffer.}
\label{fig:cn}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughput2}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_10_20_60_2.0_bw_1571241151290.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelay2}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_10_20_60_2.0_bw_1571241151290.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow that is managed by \gls{cocoa} at the bottleneck. The initial bandwidth is 20\,Mbit/s but we double after 30\,s. The delay is 10\,ms. Also a sudden large increase of bandwidth is handled well by \gls{cocoa}.}
\label{fig:cn2}
\end{figure}

@@

\begin{figure}[h]
%\subfloat[Throughput of the fq\_codel \gls{qdisc}\label{fig:fqCodelThroughputLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}
%}{}
%\subfloat[Delay of the fq\_codel \gls{qdisc}.\label{fig:fqCodelDelayLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow that is managed by fq\_codel at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 101.61\,ms. Total throughput is 2615\,MB.}
\label{fig:fqCodel}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughputLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelayLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow that is managed by \gls{cocoa} at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 130.36\,ms. Total throughput is 2893\,MB.}
\label{fig:cnLong}
\end{figure}

\begin{table}[t]
\caption{Comparison of \glspl{qdisc} for loss-based \glspl{cca} on a link of 100\;Mbit/s with an \gls{rtt} of 50\;ms. Utilization in \% of the maximum capacity; \gls{rtt} in milliseconds. For Cubic fq achieves good performance. This is because its default buffer size of 100 packets coincidentially works well for this specific link speed and \gls{rtt}.} \label{tab:performance_results}
\begin{tabular}{l r r r r r r} \toprule
& \multicolumn{2}{l}{fq} & \multicolumn{2}{l}{fq\_codel} & \multicolumn{2}{l}{\gls{cocoa}} \\
\cmidrule(r){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
& Util. & \gls{rtt} & Util. & \gls{rtt} & Util. & \gls{rtt} \\ \midrule
Cubic	& 96.2 & 54 & 92.6 & 52 & 98.5 & 66.5 \\
Reno	& 84.1 & 52.7 & 81.1 & 51.5 & 97.9 & 98.2 \\
\bottomrule
\end{tabular}
\end{table}

@@

Besides fq\_codel possibly leading to lower throughput as we have shown, another problem is that for links with a small \gls{bdp} fq\_codel can keep a standing queue akin to fq since fq\_codel only wants queuing delay to fall below 5\,ms once every 100\,ms. For example, on a link with a base \gls{rtt} of 5\,ms, fq\_codel would accept a permanent standing queue of 4.9\,ms, leading to overall \gls{rtt} being doubled, which is not required for achieving optimal throughput.

@@

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughputBBR}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_bbr_10_50_60_0.5_delay_1571288916582.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelayBBR}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_bbr_10_50_60_0.5_delay_1571288916582.pcap}}}
%}{}
\caption{Throughput and delay of a BBR~v1 flow that is managed by \gls{cocoa} at the bottleneck. The bandwidth is 50\,Mbit/s. The delay is 10\,ms and we halve it after 30\,s.}
\label{fig:cnBBR}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/cocoa_illustration_too_much.pdf}
\caption{If the buffer is too large, loss-based \glspl{cca} will keep a unnecessary standing queue which is not necessary for achieving full link utilization.}
\label{fig:tooMuch}
\end{figure}

@@

We evaluate \gls{cocoa} using the \texttt{py-virtnet} (\url{https://github.com/CN-TU/py-virtnet}) toolkit to build a virtual network using Linux's network namespaces. We initialize the buffer size for \gls{cocoa} to 100 packets per flow like in fq. The testbed consists of a sender and a receiver connected via a switch. We runs the \gls{qdisc} being tested on the interface that connects the switch to the receiver. We introduce delay with \texttt{netem} and limit bandwidth with \texttt{htb}.

\begin{figure}[h]
%\subfloat[Throughput of the fq \gls{qdisc}\label{fig:fqThroughput}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
%\subfloat[Delay of the fq \gls{qdisc}.\label{fig:fqDelay}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_cubic_10_20_60_0.5_bw_1571240937211.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow with fq at the bottleneck. The initial bandwidth is 20\,Mbit/s but it is halved after 30\,s. The delay is 10\,ms. It is clear that there is a standing queue and after the bandwidth halves, the minimum delay is 100\,ms even though 10\,ms would be possible.}
\label{fig:fq}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughput}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_10_20_60_0.5_bw_1571241047054.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelay}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_10_20_60_0.5_bw_1571241047054.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow with \gls{cocoa} at the bottleneck. The initial bandwidth is 20\,Mbit/s but we halve it after 30\,s. The delay is 10\,ms. \gls{cocoa} keeps the queuing delay minimal while achieving the same throughput as with an oversized buffer.}
\label{fig:cn}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughput2}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_10_20_60_2.0_bw_1571241151290.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelay2}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_10_20_60_2.0_bw_1571241151290.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow with \gls{cocoa} at the bottleneck. The initial bandwidth is 20\,Mbit/s but we double after 30\,s. The delay is 10\,ms. Also a sudden large increase of bandwidth is handled well by \gls{cocoa}.}
\label{fig:cn2}
\end{figure}

@@

\begin{figure}[h]
%\subfloat[Throughput of the fq\_codel \gls{qdisc}\label{fig:fqCodelThroughputLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}
%}{}
%\subfloat[Delay of the fq\_codel \gls{qdisc}.\label{fig:fqCodelDelayLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_fq_codel_cubic_100_100_240_1.0_bw_1571244312838.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow with fq\_codel at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 101.61\,ms. Total throughput is 2615\,MB.}
\label{fig:fqCodel}
\end{figure}

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughputLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelayLong}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_cubic_100_100_240_1.0_bw_1571244036720.pcap}}}
%}{}
\caption{Throughput and delay of a Cubic flow with \gls{cocoa} at the bottleneck. The bandwidth is 100\,Mbit/s. The delay is 100\,ms. The average \gls{rtt} is 130.36\,ms. Total throughput is 2893\,MB.}
\label{fig:cnLong}
\end{figure}

\begin{table}[t]
\caption{Comparison of \glspl{qdisc} for loss-based \glspl{cca} on a link of 100\;Mbit/s with an \gls{rtt} of 50\;ms. Utilization in \% of maximum capacity; \gls{rtt} in milliseconds. For Cubic fq achieves good performance. This is because its default buffer size of 100 packets coincidentially works well for this specific link speed and \gls{rtt}.} \label{tab:performance_results}
\begin{tabular}{l r r r r r r} \toprule
& \multicolumn{2}{l}{fq} & \multicolumn{2}{l}{fq\_codel} & \multicolumn{2}{l}{\gls{cocoa}} \\
\cmidrule(r){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
& Util. & \gls{rtt} & Util. & \gls{rtt} & Util. & \gls{rtt} \\ \midrule
Cubic	& 96.2 & 54 & 92.6 & 52 & 98.5 & 66.5 \\
Reno	& 84.1 & 52.7 & 81.1 & 51.5 & 97.9 & 98.2 \\
\bottomrule
\end{tabular}
\end{table}

@@

Besides fq\_codel possibly leading to lower throughput as we have shown, another problem is that for links with a small \gls{bdp} fq\_codel can keep a standing queue akin to fq since fq\_codel only wants queuing delay to fall below 5\,ms once every 100\,ms. %For example, on a link with a base \gls{rtt} of 5\,ms, fq\_codel would accept a permanent standing queue of 4.9\,ms, leading to overall \gls{rtt} being doubled, which is not required for achieving optimal throughput. 
We also ran experiments for these low \gls{bdp} scenarios: For a link speed of 20\;Mbit/s and a base \gls{rtt} of 1\;ms for a Cubic flow both \gls{cocoa} and fq\_codel achieve 98\% utilization. The average \gls{rtt} is 6.86\,ms for \gls{cocoa} and 7.31\;ms for fq\_codel.

@@

\begin{figure}[h]
%\subfloat[Throughput of \gls{cocoa}\label{fig:cnThroughputBBR}
%]{
\includegraphics[width=\columnwidth]{{{../plots/throughput_1_cn_bbr_10_50_60_0.5_delay_1571288916582.pcap}}}
%}{}
%\subfloat[Delay of \gls{cocoa}.\label{fig:cnDelayBBR}
%]{
\includegraphics[width=\columnwidth]{{{../plots/rtt_1_cn_bbr_10_50_60_0.5_delay_1571288916582.pcap}}}
%}{}
\caption{Throughput and delay of a BBR~v1 flow with \gls{cocoa} at the bottleneck. The bandwidth is 50\,Mbit/s. The delay is 10\,ms and we halve it after 30\,s.}
\label{fig:cnBBR}
\end{figure}
